---
title: "Mr E Resubmission Code"
author: "Maddie Quam"
date: "2/24/2021"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Importing the Data
```{r}
MrE_08.06.20 <- read.csv("~/Documents/Mr Elephant Analyses/MrE_08.06.20.csv", na.strings="N/A")
View(MrE_08.06.20)
```
## Assigning Variable Names
```{r}
MrE <- MrE_08.06.20
Modality <- as.factor(MrE$Modality)
Timing <- as.factor(MrE$Timing)
Success <- as.factor(MrE$Sm_Success)
SES <- as.numeric(MrE$SES..8.66.)
Age <- as.numeric(MrE$Age)
#change reference group
levels(MrE$Timing)
MrE$Timing = relevel(MrE$Timing, ref = 'Later')
Timing <- MrE$Timing
```
## Data Summary
```{r}
summary(MrE)
```

## Chi-Square Group Comparisons
```{r}
#Timing
chisq.test(Timing, Success, correct = FALSE) 
#Significant difference between Early and Later Language groups on Mr. E performance 
#Modality
chisq.test(Modality, Success, correct = FALSE) 
#No sig difference between English and ASL users on Mr. E performance
#Early Language Group Only
MrE_early <- subset(MrE, Timing=='Early')
summary(MrE_early)
chisq.test(MrE_early$Modality, MrE_early$Sm_Success, correct = FALSE)
#No significant difference between performance in Early English and Early ASL groups
#Later Language Group Only
MrE_later <- subset(MrE, Timing=='Later')
summary(MrE_later)
chisq.test(MrE_later$Modality, MrE_later$Sm_Success, correct = FALSE)
#No significant difference between performance in Later English and Later ASL groups
```
## Run Logistic Regression
```{r}
mod_1 <- glm(Success ~ Timing + SES + Modality + Age, family=binomial(link="logit"), data = MrE)
summary(mod_1)
#Timing and SES are significant predictors of Success on Mr. E, Modality and Age are not
#Odds Ratio
exp(coef(mod_1))
#Children in Early group are 2.58 times more likely to succeed on Mr. E than children in Later group
#For every 1 point increase in SES, children are 1.03 times more likely to succeed on Mr. E
```
## Check Interactions
```{r}
#Timing*Modality
mod_int1 <- glm(Success ~ Timing * Modality + SES + Age, family=binomial(link="logit"), data = MrE)
summary(mod_int1)
#Timing*Age
mod_int2 <- glm(Success ~ Timing * Age + Modality + SES, family=binomial(link="logit"), data = MrE)
summary(mod_int1)
#Neither of these interactions are significant
```
## Model Comparisons
```{r}
#First compare the interaction models to the original model
anova(mod_1, mod_int1, test = 'LR')
anova(mod_1, mod_int2, test = 'LR')
#Neither of the models that include an interaction are a better fit than the original model
#Does Timing explain variability in Mr. E performance independently of SES?
#model without Timing as a predictor variable
mod_no_timing <- glm(Success ~ SES + Modality + Age, family=binomial(link="logit"), data = MrE)
summary(mod_no_timing)
#Next compare this model without Timing to the original model
anova(mod_no_timing, mod_1, test = 'LR')
#Timing definitely does!
```
## Logistic Regression Results Table
```{r}
library(stargazer)
stargazer(mod_1, type = "text", title = "Logistic Regression Results", align=TRUE, dep.var.labels=c("Mr. Elephant Performance"), 
          covariate.labels=c("Timing (Early)", "Socioeconomic Status", "Modality (English)", "Age"), 
          single.row=TRUE, keep.stat=c("n", "aic"),  out= "MrE_original_model_210211.htm")
```
## Age Dot Box Plot
```{r}
library(ggplot2)
SuccessNewLabels <- c("Did Not Get Both Trials Correct", "Both Trials Correct")
ggplot(data=MrE, mapping = aes(x= Success, y=Age)) + geom_boxplot() +
  geom_dotplot(dotsize=.9, binaxis = "y", stackdir = "center") +
  stat_summary(fun=mean, geom="point", shape=18, size=6, color="red") + 
  theme(axis.text.x = element_text(color = "grey20", size = 14, hjust = .5, vjust = .5, face = "plain"),
        axis.text.y = element_text(color = "grey20", size = 14, hjust = 1, vjust = 0, face = "plain"),
        axis.title.x = element_text(color = "grey20", size = 16, hjust = .5, vjust = 0, face = "plain"),
        axis.title.y = element_text(color = "grey20", size = 16, hjust = .5, vjust = .5, face = "plain")) + 
  ylab("Age (years)") + scale_x_discrete(labels= SuccessNewLabels) + 
  xlab("Performance on Mr. Elephant Small Quantity Trials")
```

### Exploratory Follow Up Analyses
## Import Data and Assign Variable Names
```{r}
MrE_NA_Omit_07.20.20 <- read.csv("~/Documents/Mr Elephant Analyses/MrE_NA_Omit_07.20.20.csv", na.strings="N/A")
View(MrE_NA_Omit_07.20.20)
MrE <- MrE_NA_Omit_07.20.20
Modality <- as.factor(MrE$Modality)
Timing <- as.factor(MrE$Timing)
Success <- as.factor(MrE$Sm_Success)
SES <- as.numeric(MrE$SES..8.66.)
Age <- as.numeric(MrE$Age)
Highest_Count <- as.numeric(MrE$HC_noobj)
CP_Knower <- as.factor(MrE$CP.Knower)
#change reference groups
levels(MrE$CP.Knower)
MrE$CP.Knower = relevel(MrE$CP.Knower, ref = 'SS')
CP_Knower <- MrE$CP.Knower
levels(MrE$Timing)
MrE$Timing = relevel(MrE$Timing, ref = 'Later')
Timing <- MrE$Timing
```
## Does Mr. E predict Give-N?
# Run Logistic Regression
```{r}
mod_GN <- glm(CP_Knower ~ Success + Timing + SES + Age, family=binomial(link="logit"), data = MrE)
summary(mod_GN)
stargazer(mod_GN, type = "text", title = "Logistic Regression Results", align=TRUE, dep.var.labels=c("Give-N CP Knower Level"), 
          covariate.labels=c("Mr. Elephant Performance", "Timing (Early)", "Socioeconomic Status", "Age"), 
          single.row=TRUE, keep.stat=c("n", "aic"),  out= "GN_MrE_model_210215.htm")
#Is the addition of Mr. E significant to Give-N performance?
#model without Mr. E Success as predictor variable
mod_GN2 <- glm(CP_Knower ~ Timing + SES + Age, family=binomial(link="logit"), data = MrE)
summary(mod_GN2)
#Next compare this model without Mr. E Success to the previous model
anova(mod_GN2, mod_GN, test = 'LR')
#Addition of Mr. E performance to the model is significant
```
## Does Give-N and Highest Count predict Mr. E?
```{r}
#First run original model with subset of participants who completed Mr. E, Give-N and Highest Count
mod_original <- glm(Success ~ Timing + SES + Modality + Age, family=binomial(link="logit"), data = MrE)
summary(mod_original) #same results, Timing and SES significant predictors
#Next at Give-N and Highest Count as predictors
mod_all <- glm(Success ~ Timing + SES + Modality + Age + CP_Knower + Highest_Count, family=binomial(link="logit"), data = MrE)
summary(mod_all) #Timing and Give-N significant predictors
#remove nonsignificant predictors (Modality and Age)
mod_explore <- glm(Success ~ Timing + SES + CP_Knower + Highest_Count, family=binomial(link="logit"), data = MrE)
summary(mod_explore) #better AIC than the previous model
#Compare models with and without Modality and Age
anova(mod_explore, mod_all, test = 'LR') 
#Modality and Age do not contribute significantly to the model, so we'll leave them out
#Odds Ratio
exp(coef(mod_explore))
```
#Compare Models
```{r}
#Compare models with and without addition of Give-N and Highest Count
anova(mod_original, mod_all, test = 'LR')
#Addition of Give-N and Highest Count are significant to model
#Does Highest Count explain any variance in Mr. E performance?
#model without Highest Count
mod_no_hc <- glm(Success ~ Timing + SES + CP_Knower, family=binomial(link="logit"), data = MrE)
summary(mod_no_hc)
#Compare models with and without Highest Count
anova(mod_no_hc, mod_explore, test = 'LR')
#Highest Count is not a significant addition to the model
```
## Logistic Regression Results Table
```{r}
stargazer(mod_explore, type = "text", title = "Logistic Regression Results", align=TRUE, dep.var.labels=c("Mr. Elephant Performance"), 
          covariate.labels=c("Timing (Early)", "Socioeconomic Status", "Give-N (CP-Knower)", "Highest Count"), 
          single.row=TRUE, keep.stat=c("n", "aic"),  out= "MrE_exploratory_model_210218.htm")
```
